---
title: 'Machine Learning: Problem Set 2'
author: "Paulino Diaz"
date: "January 31, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(wooldridge)
library(boot)
knitr::opts_chunk$set(echo = TRUE)
```

## Q1
We cna choose the function

```{r, q1}
set.seed(1)
x1 <- rnorm(1000, mean = 0, sd = 1)
x2 <- rnorm(1000, mean = 0, sd = 1)

data <- tibble(x1 = x1,
               x2 = x2,
               y = -abs(x1^2) + x2^2)

summary(lm(y ~ x1 + x2, data))

```

## Q2
```{r, q2, include=F}
data(catholic); attach(catholic)
female <- as.factor(female); gender = revalue(female, c("1" = "female", "0" = "male"))
hsgrad <- as.factor(hsgrad); hs = revalue(hsgrad, c("1" = "highschool", "0" = "no_highschool"))

catholic <- catholic %>%
  filter(!is.na(hsgrad))

```

```{r, q2a}
summary(lm(read12 ~ female, catholic))
```

The coefficient for female can be interpreted as the difference in average reading scores between males and females.

```{r, q2b}
summary(lm(read12 ~ female - 1, catholic))
```

The coefficient on female can be interpreted as the average reading score for females.

```{r, q2c}
summary(lm(read12 ~ female*hsgrad, catholic))
```
For this model: 
* The intercept is the average reading score for males who have not finished highschool. 
* The female coefficient is the difference in average reading scores between males and females who have not attended highschool. 
* The hsgrad coefficient is the difference in average reading scores between males who have attended highschool and those who haven't
* The interaction coefficient is the difference in average reading scores between males with a highschool diploma and females with a highschool diploma

```{r, q2d}
summary(lm(read12 ~ female*lfaminc, catholic))
```
In this model:
* The intercept is the average reading score when the family income = 1 and the individual is male.
*The female coefficient is the difference in average reading scores between males and females when family income = 1.
*The coefficient of log(family income) multiplied by 1/100 is equal to the average precentage change in reading scores due to a 1 percent increase in family income when the individual is male.
*The coefficient of the interaction multiplied by 1/100 is equal to the difference in percentage change in reading scores due to a 1 percent change in family income, between males and females.

